\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-14 draft.tex
write model basics: payoff functions

The model is based on that of Banks (2000)

@@

>>>>

The model is based on Banks' (2000) model of vote buying in a legislature, which is in turn a discrete version of Groseclose and Snyder's (1996) model with a continuum of legislators. The major difference here is the addition of uncertainty about the legislator's ideal points.

Each of three legislators faces a choice between the status quo, $x$ and a new policy proposal $s$. The utility function of legislator $i$ is given by $v(i) = u_i(x) - u_i(s)$, which is measured in money units. Note that legislators only have preferences about how they vote, not over which alternative wins.

There are two vote buyers labeled $A$ and $B$ who each prefers to maximize the expected value of his preferred policy net of the bribes he has to pay. $A$ prefers policy $x$ and has willingness to pay (WTP) $W_A$ for $x$ measured in money and values $s$ at zero. $B$ prefers $s$and has WTP $W_B$ for $s$. Each vote buyer would prefer to concede the issue rather than pay more than his WTP.

Vote Buyer $A$ moves first, providing a bribe offer function $a(i)$. $a(i)$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b(i)$. Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff. I assume unbribed legislators who are indifferent vote for $s$ and that all bribed legislators who are indifferent vote for whoever bribed them last.

(Remember that I've assumed a very specific functional form)

@@

Goal: characterize SPNE in pure strategies
